paper2_resistance_mechanisms_mixtures

### 2016-11-25 inst/documents/paper2_resistance_mechanisms_mixtures.Rmd
bump version

---
title: "paper2_resistance_mechanisms_mixtures"
output: pdf_document
#output: word_document
author: "Andy South, Ian Hastings and Bethany Levick"
date: "`r Sys.Date()`"
---

@@

### version 6

>>>>

---
title: "paper2_resistance_mechanisms_mixtures"
output: pdf_document
#output: word_document
author: "Andy South and Ian Hastings"
date: "`r Sys.Date()`"
---

@@

### version 7
